\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage[margin=2cm]{geometry}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2ex}

\author{Wan Shi Tong -- He Who Knows Ten Thousand Things}
\title{Permission Request}
\date{version: \today}
\begin{document}
\maketitle

I, \rule{15em}{.4pt} \textcolor{gray}{(full name)} \rule{10em}{.4pt} \textcolor{gray}{(date of birth)} as a member of this group, acknowledge the fact that the permission to access to the group's central, \LaTeX{} bibliography repository has advantages, but it also comes with several responsibilities. I understand that maintaining this repository is a mutual endeavor; hence I am responsible for any changes I will or going to push into it. Therefore, I have to correct any mistakes or errors, which I cause as soon as possible to prevent any harm to my fellow group members.

By getting the permission to read the repository, I am allowed to use the collected bibliography of the group in any of my present and further publications. Write permission entitles me to add any bibliographical entries to the repository, which I consider useful. Furthermore, I am allowed to fix or modify any errors in the central repository. I acknowledge that the implementation and the execution of these actions are my tasks, and I have to accomplish them personally, with the best of my intentions. 

I guarantee that I got familiar with any presently available documentations, and I will follow any further instructions, guides, and documentation related to the usage and maintenance of the repository. I understand that I may have to learn new technologies and tools that are required to achieve these tasks. I acknowledge that the duration of these tasks and the learning curve's steepness depend on my prior knowledge about the utilized technologies. I understand that various features of the system contained in the repository require me to install additional software components onto my local system.

\textbf{I commit myself, that I neither will nor going to do anything, which hinders my fellow group members' work in the usage of this bibliographical database.}

With the knowledge and understanding of the above-detailed rights and responsibilities, I request read and write permission to the group's central, \LaTeX{} bibliography repository.\vspace*{10ex}

\parbox{.33\linewidth}{\centering\dotfill\\\textcolor{gray}{(date)}}\hfill
\parbox{.33\linewidth}{\centering\dotfill\\\textcolor{gray}{(signature)}}
\end{document}